### 2022-08-12 paper/Chapters/Chapter04.tex
update paper

\begin{figure}[!h]
	\centering
	\captionsetup{width=\linewidth}
	{\includegraphics[width=0.49\textwidth]{./Figures/Data_Extreme.png}}
	{\includegraphics[width=0.49\textwidth]{./Figures/Data_Range.png}}
	\decoRule
	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
	\label{fig:data_range}
\end{figure}

\begin{table}[th]

	\centering
	\begin{tabular}{c | c c c}
		\toprule
		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
		\midrule
		X & 1.48 & -0.75 & 0.73\\
		\hline 
		Y & 1.56 & -0.76 & 0.80\\
		\hline 
		Z & 1.47 & 6.53 & 8.00\\
		\bottomrule
	\end{tabular}
	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. }
	\label{tab:data_range}
\end{table}

>>>>

\begin{figure}[!h]
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{0.49\linewidth}
		\includegraphics[width=\textwidth]{./Figures/Data_Extreme.png}
		\caption{Extreme Values in each axis }
	\end{subfigure}
	\begin{subfigure}[b]{0.49\linewidth}
		\includegraphics[width=\textwidth]{./Figures/Data_Range.png}
		\caption{Vertex Range in each axis}
	\end{subfigure}
	\decoRule
	\caption{The position fluctuation of the points in 100 Vertex Maps. 
		Left: Extreme values in 3 axes; Right: Vertex range in 3 axis.}
	\label{fig:data_range}
\end{figure}

\begin{table}[th]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{c | c c c}
		\toprule
		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
		\midrule
		X & 1.48 & -0.75 & 0.73\\
		\hline 
		Y & 1.56 & -0.76 & 0.80\\
		\hline 
		Z & 1.47 & 6.53 & 8.00\\
		\bottomrule
	\end{tabular}
	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. }
	\label{tab:data_range}
\end{table}
